The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
disc implic f pract

\newpage
\section{Discussion} \label{discussion}
In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.

\newpage
\subsection{RQ1 Answer}

Our results show that the major driving force for change in APIs is the push (!!!reword) for functionality. The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add brand-new (!!!reword) modules or adding functionality to existing modules were the most common. We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes which were related to functionality. Following this line of thought, the hunger (!!!reword?) for functionality can be seen as a catalyst for other driving forces to occur (!!!reword). The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws. In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory". The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.

@@

\subsection{Implications for Practitioners}
%       -How will our study help Axis? (More important)
The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed. [1980programs]

@@

--------------------------------------------------------------------------

>>>>

\section{Discussion} \label{discussion}
In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.

\subsection{RQ1 Answer}  
Our results show that the major driving force for change in APIs is the push (!!!reword) for functionality. The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add brand-new (!!!reword) modules or adding functionality to existing modules were the most common. We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes which were related to functionality. Following this line of thought, the hunger (!!!reword?) for functionality can be seen as a catalyst for other driving forces to occur (!!!reword). The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws. In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory". The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.

@@

\subsection{Implications for Practitioners}
The changes introduced to the API are mainly based on the expertise and experiences of the API architects at the case company. There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed. With our work, we hope to provide a new angle of analysis

------------------------------------------------------------------------

%       -How will our study help Axis? (More important)
The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed. [1980programs]

@@
